Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-19 doc/JFLA2022/Slides/Slides.tex
Slides (small changes)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}
    \frametitle{Paths and accessibility}
    \begin{block}{ }
      % If $\beta<\alpha<\epsilon_0$, there exists $i$ and $l$ in $\mathbb{N}$ such that $ \alpha \rplus{i, i+1, i+2, \dots,l} \beta$.

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles
  (stronger than \textcolor{banyuls}{Banyuls 2018}).}

@@

\begin{frame}[fragile]

@@

  \begin{block}{Theorems}
    \begin{itemize}
    \item \textcolor{mathcolor}{$F_\alpha$} is primitive recursive iff \textcolor{mathcolor}{$\alpha<\omega$}.
     \item  
    The function which computes the length of hydra battles
    for \textcolor{mathcolor}{$\alpha$} (according to the initial index) is not primitive recursive
    (for $\textcolor{mathcolor}{\alpha\geq \omega^\omega}$).
    \end{itemize}

@@

  \end{block}
  % \begin{block}{}
  %   We experiment also the other direction (importing \texttt{ssete9} lemmas to \Hydras).
  % \end{block}
\end{frame}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label={accessibility}]

    \frametitle{Paths and accessibility}
    \begin{block}{ }
      % If $\beta<\alpha<\epsilon_0$, there exists $i$ and $l$ in $\mathbb{N}$ such that $ \alpha \rplus{i, i+1, i+2, \dots,l} \beta$.

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles
  (stronger than \textcolor{banyuls}{Banyuls 2018}).
}

@@

\begin{frame}[fragile, label={fgflemmas}]

@@

\begin{frame}[label={fgftheorems}]
\label{thms-fastgrowing}
  \begin{block}{Theorems}
    \begin{itemize}
    \item \textcolor{mathcolor}{$F_\alpha$} is primitive recursive iff \textcolor{mathcolor}{$\alpha<\omega$}.
     \item  
    The function which computes the length of hydra battles
    for \textcolor{mathcolor}{$\alpha$} (according to the initial index) is not primitive recursive
    (for $\textcolor{mathcolor}{\alpha\geq \omega^\omega}$).
    \end{itemize}

@@

  \end{block}
  The lemmas mentionned in previous slides (accessibility, fast growing functions) are ``ported'' this way from \texttt{Hydra-battles}   into \texttt{Gaia-Hydras}.
  % \begin{block}{}
  %   We experiment also the other direction (importing \texttt{ssete9} lemmas to \Hydras).
  % \end{block}
\end{frame}

### 2022-06-19 doc/JFLA2022/Slides/gcanonSLE.tex
Slides (small changes)

\begin{alectryon}
  % Generator: Alectryon
  \sep
  \begin{sentence}
    \begin{input}
      \PY{k+kn}{Lemma}~\PY{n+nf}{canonS\PYZus{}LE}~\PY{n+nv}{a}~\PY{n+nv}{n}\PY{o}{:}\nl
      ~~~~\PY{n}{T1nf}~\PY{n}{a}~\PY{o}{\PYZhy{}\PYZgt{}}~\PY{n}{canon}~\PY{n}{a}~\PY{n}{n}\PY{o}{.+}\PY{l+m+mi}{1}~\PY{o}{\PYZlt{}=}~\PY{n}{canon}~\PY{n}{a}~\PY{n}{n}\PY{o}{.+}\PY{l+m+mi}{2}\PY{o}{.}\nl
    \end{input}
  \end{sentence}
  \sep
  \begin{sentence}
    \begin{input}
      \PY{k+kn}{Proof}\PY{o}{.}\nl
    \end{input}
  \end{sentence}
  \sep
  \begin{sentence}
    \begin{input}
      ~~\PY{n+nb}{rewrite}~\PY{o}{\PYZhy{}(}\PY{n}{h2g\PYZus{}g2hK}~\PY{n}{a}\PY{o}{)}~\PY{o}{\PYZhy{}}\PY{n}{nf\PYZus{}ref}~\PY{o}{/}\PY{n}{canon}~\PY{n}{g2h\PYZus{}h2gK}~\PY{o}{=\PYZgt{}}~\PY{n}{Hnf}\PY{o}{;}\nl
      ~~\PY{n+nb+bp}{by}~\PY{n+nb}{apply}~\PY{n}{le\PYZus{}ref}\PY{o}{,}~\PY{n}{canonS\PYZus{}LE}\PY{o}{.}~\nl
    \end{input}
  \end{sentence}
  \sep
  \begin{sentence}
    \begin{input}
      \PY{k+kn}{Qed}\PY{o}{.}
    \end{input}
  \end{sentence}
\end{alectryon}

>>>>

\begin{alectryon}
  % Generator: Alectryon
  \sep
  \begin{sentence}
    \begin{input}
      \PY{k+kn}{Lemma}~\PY{n+nf}{canonS\PYZus{}LE}~\PY{n+nv}{a}~\PY{n+nv}{n}\PY{o}{:}~\PY{n}{T1nf}~\PY{n}{a}~\PY{o}{\PYZhy{}\PYZgt{}}~\PY{n}{canon}~\PY{n}{a}~\PY{n}{n}\PY{o}{.+}\PY{l+m+mi}{1}~\PY{o}{\PYZlt{}=}~\PY{n}{canon}~\PY{n}{a}~\PY{n}{n}\PY{o}{.+}\PY{l+m+mi}{2}\PY{o}{.}\nl
    \end{input}
  \end{sentence}
  \sep
  \begin{sentence}
    \begin{input}
      \PY{k+kn}{Proof}\PY{o}{.}\nl
    \end{input}
  \end{sentence}
  \sep
  \begin{sentence}
    \begin{input}
      ~~\PY{n+nb}{rewrite}~\PY{o}{\PYZhy{}(}\PY{n}{h2g\PYZus{}g2hK}~\PY{n}{a}\PY{o}{)}~\PY{o}{\PYZhy{}}\PY{n}{nf\PYZus{}ref}~\PY{o}{/}\PY{n}{canon}~\PY{n}{g2h\PYZus{}h2gK}~\PY{o}{=\PYZgt{}}~\PY{n}{Hnf}\PY{o}{;}\nl
      ~~\PY{n+nb+bp}{by}~\PY{n+nb}{apply}~\PY{n}{le\PYZus{}ref}\PY{o}{,}~\PY{n}{canonS\PYZus{}LE}\PY{o}{.}~\nl
    \end{input}
  \end{sentence}
  \sep
  \begin{sentence}
    \begin{input}
      \PY{k+kn}{Qed}\PY{o}{.}
    \end{input}
  \end{sentence}
\end{alectryon}
